\documentclass{article}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{fontawesome5} % for icons

% Define colors
\definecolor{darkblue}{rgb}{0.0, 0.0, 0.55}

% Set up hyperlinks
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    filecolor=darkblue,      
    urlcolor=darkblue,
}

% Page margins
\geometry{
    a4paper,
    total={210mm,297mm},
    left=20mm,
    right=20mm,
    top=20mm,
    bottom=20mm,
}

\begin{document}

\begin{center}
    \textbf{\Huge Samarth Prabhu} \\
    \vspace{2mm}
    \faMapMarker \ Mumbai, India \quad
    \faPhone \ (+91) 8169143075 \quad
    \faEnvelope \ prabhusamarth001@gmail.com \\
    \href{https://samarth745.github.io/Portfolio-Website/}{Portfolio} \quad 
    \href{https://in.linkedin.com/in/samarth-prabhu}{LinkedIn} % Add LinkedIn profile link with custom name
\end{center}

\section*{PROFESSIONAL SUMMARY}
Experienced Data Analyst and Business Intelligence at Quantum Link communication with 2 years of experience in business analytics, data mining, data modeling, and data visualization. Skilled in leveraging data analysis and reporting to drive business decisions and ensure accuracy of information. Proven ability to quickly identify trends and generate data-driven insights.

\section*{DATA SCIENCE EXPERIENCE}
\textbf{Data Analyst and Business Intelligence | Quantum Link communication | Mumbai | August 2022 - Present}
\begin{itemize}[leftmargin=*]
    \item Achieved 80\% accuracy in forecasting active customer trends by developing predictive models based on usage patterns.
    \item Reduced market analysis time by 10+ hours through data-driven automated analysis, enhancing marketing strategies and boosting campaign outcomes.
    \item Produced comprehensive business dashboards in Power BI, aiding in data-driven decision-making processes.
    \item Spearheaded initiatives to automate data workflows, significantly optimizing operational efficiency by creating 10+ metrics while weaving together a more comprehensive data narrative.
    \item Utilized Google Ads API for streamlined data retrieval, automating the process of obtaining critical information.
\end{itemize}

\vspace{5mm} % Add white space

\noindent % Prevent indentation for the following section
\textbf{Business Analyst | Sciative Solutions | Navi Mumbai | June 2021 - February 2022}
\begin{itemize}[leftmargin=*]
    \item Devised and executed data-driven pricing strategies, leveraging in-depth data analysis to optimize revenue streams for clients, resulting in a 12\% average increase in revenue.
    \item Conducted comprehensive pricing audits for diverse clients, analyzing historical sales data and market trends to identify pricing gaps and opportunities for profitability enhancement.
    \item Created a dynamic pricing audit model using adding new metrics to original data python, contributing to a 50\% reduction in Audit timings.
    \item Designed and delivered client-facing presentations showcasing pricing recommendations, data-driven insights, and actionable strategies to improve their pricing competitiveness.
    \item Onboarded 5+ clients in the AI system for smooth functioning.
\end{itemize}

\section*{EDUCATION}
\textbf{Masters in Mathematics | Mumbai University | Mumbai | 2021 | 6.2}
\newline
\textbf{Bachelors in Mathematics | Jai Hind College | Minor in Physics | Mumbai | 2019 | 8.4}

\section*{SKILLS}
\begin{itemize}[leftmargin=*]
    \item \textbf{Data Retrieval and Processing Tools:} SQL, Python, Excel
    \item \textbf{Data Visualization:} Power BI, Excel
    \item \textbf{Statistical and Data Science:} Hypothesis testing, Advance Statistical Methods, Machine Learning, Time Series Analysis, Reinforcement Learning, Natural Language Processing
    \item \textbf{Web Scraping:} Beautiful Soup, Selenium
    \item \textbf{Deployment:} Flask (API), Streamlit
\end{itemize}

\end{document}
